Hydrodynamics and rheology of an adhesive vesicle doublet

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
fixing Fig 6
fixed fig 1
fixed up figure 6
2nd edits from yny

\begin{figure}[htp]
  \begin{minipage}{0.53\textwidth}
    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
  \end{minipage}
   \caption{\label{fig:InclinationAngle} The
  definition of the inclination angle of a vesicle doublet at the center of an extensional flow.  
  An inclination angle of $\pi$
  indicates a doublet whose long axis is parallel to the diverging
  direction, while an inclination angle of $\pi/2$ indicates a doublet
  whose short axis is parallel to the diverging direction.  The square
  mark is a stagnation point and the round point is located at the
  center of the vesicle.}
\end{figure}

@@

Finally, to further characterize the rotating dynamics of a doublet, we
compute and plot the vorticity and total force on the vesicles in
Figure~\ref{fig:extensionalVorticity}. We consider the doublet formed
with a two vesicles of reduced area $\Delta A = 0.7$, adhesion length
scale $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
extensional rate $\chi = 0.7$.  The doublet's inclination angle remains
close to $\pi$ for a period of time (see the left plot of
Figure~\ref{fig:extensionalInclinationAngle}).  Then, as the doublet
starts to rotate, the total force first points in the direction of the
diverging direction and then rotates until it is parallel with the
vesicles' long axis.  This results in a shearing motion between the
vesicles that results in a recoil type motion near $t=295$.  Finally,
the vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A = 0.7$,
  the extensional rate is $\chi = 0.7$, the adhesion length scale is
  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
\end{figure}

>>>>

\begin{figure}[htp]
    \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
    \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is parallel to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   parallel to the diverging direction.  The square mark is a stagnation
   point and the round point is located at the center of the vesicle.}
   \end{figure}

@@

Finally, to further characterize the rotating dynamics of a doublet in the fluid trap, we
compute and plot the vorticity and total force on a doublet with identical vesicles
with reduced area $\Delta A=0.7$, adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
extensional rate $\chi = 0.7$ in Figure~\ref{fig:extensionalVorticity}.
Starting from a doublet inclination angle $\theta=\pi/2$, 
the vesicle doublet slowly begins to rotate around $t\sim 265$
(see the left plot of
Figure~\ref{fig:extensionalInclinationAngle}).  We notice that the net force on each vesicle is almost 
anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the vesicles apart.

Then, as the doublet
starts to rotate, each vesicle experiences drag force from both up and down diverging streaming flows.
For small extensional rate, the rotation will continue until $\theta = \pi$ so the doublet remains perfectly symmetric
with respect to their mid-plane  and each vesicle experiences drag forces that cancel in both directions.
For slightly higher extensional rate, we observe that the two vesicles slide against each other as the doublet rotate.
The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to a sigmoidal profile of nearly uniform height.
This adjustment greatly reduces the net force on each vesicle, leading to an equilibrium configuration with an inclination angle $\theta < \pi$ as shown in 
the left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally,
the vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A = 0.7$,
  the extensional rate is $\chi = 0.7$, the adhesion length scale is
  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
\end{figure}
